---
title: "Google Ads Data"
author: "Fabio Votta"
output:
  html_document:
    toc: true
    toc_float: true
---

## Packages and Folders

```{r}
# Install these packages if you don't have them yet
# if (!require("pacman")) install.packages("pacman")
# devtools::install_github("favstats/tidytemplate")

knitr::opts_chunk$set(warning = F, message = F)

options(scipen = 999)

pacman::p_load(tidyverse, tidytemplate, countrycode)

# Creates folders
# tidytemplate::data_dir()
# tidytemplate::images_dir()
```


## Load Data

```{r, data}

ggl_ads <- read_csv("data/google-political-ads-creative-stats.csv")%>% 
  mutate(Regions = str_remove_all(Regions, "EU|,") %>% str_trim)  %>% 
  mutate(cntry = countrycode::countrycode(Regions, origin = "iso2c", destination = "country.name"))  %>%
  janitor::clean_names()   %>% 
  mutate(spend = map2(as.list(spend_range_min_usd), as.list(spend_range_max_usd), c)) %>% 
  mutate(spend = spend %>% map_dbl(median)) %>% 
  mutate(age_targeting2 = as.factor(age_targeting) %>% as.numeric) %>% 
  mutate(gender_targeting2 = as.factor(gender_targeting) %>% as.numeric) %>% 
  mutate(age_targeted = !(age_targeting2 %in% c(47, 10)), 
         gender_targeted = !(gender_targeting2 %in% c(7, 5)), 
         region_targeted = !(geo_targeting_included %in% c("Not targeted") & geo_targeting_excluded %in% c("Not targeted")),
         male = str_detect(gender_targeting, 'Male'), 
         female = str_detect(gender_targeting, 'Female')) %>%
  glimpse()

```

## Date range of data

Earliest run date:

```{r}
min(ggl_ads$first_served_timestamp, na.rm = T)
```

Latest run date:

```{r}

max(ggl_ads$last_served_timestamp, na.rm = T)
```

## Number of countries

```{r}
ggl_ads %>% 
  distinct(cntry) %>% 
  nrow
```


## Number of Ads

```{r}
nrow(ggl_ads)
```


## Number of Political ads

```{r}

ggl_ads %>% 
  count(cntry, sort = T) %>% 
  # filter(str_count(Regions)==2)%>% 
  mutate(cntry = fct_reorder(cntry, n)) %>% 
  drop_na(cntry) %>% 
  ggplot(aes(cntry, n)) +
  geom_col() +
  coord_flip() +
  labs(y = "\nNumber of Political Ads on Google", x = "") +
  theme_minimal()

```



## Most spend per ad

```{r}
spend_dat <- ggl_ads %>% 
  group_by(cntry) %>% 
  summarize(mean_spend_per_ad = mean(spend, na.rm = T),
            median_spend_per_ad = median(spend, na.rm = T))

spend_dat %>% 
  mutate(cntry = fct_reorder(cntry, mean_spend_per_ad)) %>% 
  drop_na(cntry) %>% 
  ggplot(aes(cntry, mean_spend_per_ad)) +
  geom_col() +
  coord_flip() +
  labs(y = "\nDollars spent per Political Ad on Google", x = "") +
  theme_minimal()
```


## Most active advertiser

```{r}
ggl_ads %>% 
  count(advertiser_name, sort = T)%>% 
  mutate(perc = round(n/sum(n) * 100, 2)) %>% 
  slice(1:10)
```

## Most common categories for gender targeting

```{r}
ggl_ads %>% 
  count(gender_targeting, sort = T) %>% 
  mutate(perc = round(n/sum(n) * 100, 2))
```

## Most common categories for age targeting

```{r}
ggl_ads %>% 
  count(age_targeting, sort = T) %>% 
  mutate(perc = round(n/sum(n) * 100, 2))
```

## Most common categories for geo targeting

```{r}
ggl_ads %>% 
  count(geo_targeting_included, sort = T) %>% 
  mutate(perc = round(n/sum(n) * 100, 2))
```






## Age Targeting

```{r}
ggl_ads %>% 
  count(age_targeted, sort = T) %>% 
  mutate(total = sum(n)) %>% 
  mutate(perc = round(n/total*100,2))
  
```

## Gender Targeting

```{r}
ggl_ads %>% 
  count(gender_targeted, sort = T) %>% 
  mutate(total = sum(n)) %>% 
  mutate(perc = round(n/total*100,2))
```


## Region Targeting

```{r}
ggl_ads %>% 
  count(region_targeted, sort = T) %>% 
  mutate(total = sum(n)) %>% 
  mutate(perc = round(n/total*100,2))
```


## Targeting per Country


```{r}


fin_dat <- ggl_ads %>%
  group_by(advertiser_id, advertiser_name, cntry) %>%
  summarize(mean_spend_per_ad = mean(spend, na.rm = T),
            median_spend_per_ad = median(spend, na.rm = T),
            prop_age_targeted = mean(as.numeric(age_targeted), na.rm = T),
            prop_gender_targeted = mean(as.numeric(gender_targeted), na.rm = T),
            prop_region_targeted = mean(as.numeric(region_targeted), na.rm = T),
            prop_female_targeted = mean(as.numeric(female & !male), na.rm = T),
            prop_male_targeted = mean(as.numeric(male & !female), na.rm = T), 
            sum_expense = sum(spend_range_max_usd),
            n_add = n()) %>%
  arrange(-prop_male_targeted)
```

### Age Range

```{r}
fin_dat %>% 
  ungroup() %>% 
  filter(n_add >= 100) %>% 
  arrange(desc(prop_age_targeted)) %>% 
  group_by(cntry) %>% 
  summarize(prop_age_targeted = mean(prop_age_targeted)) %>% 
  drop_na() %>% 
  mutate(cntry = fct_reorder(cntry, prop_age_targeted)) %>% 
  drop_na(cntry) %>% 
  ggplot(aes(cntry, prop_age_targeted)) +
  geom_col() +
  coord_flip() +
  labs(y = "\nAverage Proportion of Ads that are targeting a specific Age Range", x = "") +
  theme_minimal()
```

### Female but not male

```{r}
fin_dat %>% 
  ungroup() %>% 
  filter(n_add >= 100) %>% 
  arrange(desc(prop_gender_targeted)) %>% 
  group_by(cntry) %>% 
  summarize(prop_gender_targeted = mean(prop_gender_targeted)) %>% 
  drop_na() %>% 
  mutate(cntry = fct_reorder(cntry, prop_gender_targeted)) %>% 
  drop_na(cntry) %>% 
  ggplot(aes(cntry, prop_gender_targeted)) +
  geom_col() +
  coord_flip() +
  labs(y = "\nAverage Proportion of Ads that are targeting a specific Gender", x = "") +
  theme_minimal()
```


### Male but not female

```{r}
fin_dat %>% 
  ungroup() %>% 
  filter(n_add >= 100) %>% 
  arrange(desc(prop_male_targeted)) %>% 
  group_by(cntry) %>% 
  summarize(prop_male_targeted = mean(prop_male_targeted)) %>% 
  drop_na() %>% 
  mutate(cntry = fct_reorder(cntry, prop_male_targeted)) %>% 
  drop_na(cntry) %>% 
  ggplot(aes(cntry, prop_male_targeted)) +
  geom_col() +
  coord_flip() +
  labs(y = "\nAverage Proportion of Ads that are targeting Male users", x = "") +
  theme_minimal()
```

### Region

```{r}
fin_dat %>% 
  ungroup() %>% 
  filter(n_add >= 100) %>% 
  arrange(desc(prop_female_targeted)) %>% 
  group_by(cntry) %>% 
  summarize(prop_female_targeted = mean(prop_female_targeted)) %>% 
  drop_na() %>% 
  mutate(cntry = fct_reorder(cntry, prop_female_targeted)) %>% 
  drop_na(cntry) %>% 
  ggplot(aes(cntry, prop_female_targeted)) +
  geom_col() +
  coord_flip() +
  labs(y = "\nAverage Proportion of Ads that are targeting Female users", x = "") +
  theme_minimal()
```

```{r}
fin_dat %>% 
  ungroup() %>% 
  filter(n_add >= 100) %>% 
  arrange(desc(prop_region_targeted)) %>% 
  group_by(cntry) %>% 
  summarize(prop_region_targeted = mean(prop_region_targeted)) %>% 
  drop_na() %>% 
  mutate(cntry = fct_reorder(cntry, prop_region_targeted)) %>% 
  drop_na(cntry) %>% 
  ggplot(aes(cntry, prop_region_targeted)) +
  geom_col() +
  coord_flip() +
  labs(y = "\nAverage Proportion of Ads that are targeting a specific Region", x = "") +
  theme_minimal()
```

## Microtargeting per Country



### Age

```{r, results='asis'}
fin_dat %>% 
  ungroup() %>% 
  filter(n_add >= 100) %>% 
  group_by(cntry)  %>% 
  arrange(cntry, desc(prop_age_targeted)) %>% 
  slice(1:10) %>%
  filter(prop_age_targeted != 0) %>% 
  select(advertiser_name, cntry, mean_spend_per_ad, prop_age_targeted, prop_gender_targeted, prop_region_targeted) %>% 
  group_split(cntry) %>% 
  map(knitr::kable)
  
```

### Gender

```{r, results='asis'}
fin_dat %>% 
  ungroup() %>% 
  filter(n_add >= 100) %>% 
  group_by(cntry)  %>% 
  arrange(cntry, desc(prop_gender_targeted)) %>% 
  slice(1:10) %>%
  filter(prop_gender_targeted != 0) %>% 
  select(advertiser_name, cntry, mean_spend_per_ad, prop_age_targeted, prop_gender_targeted, prop_region_targeted) %>% 
  group_split(cntry) %>% 
  map(knitr::kable)
  
```

### Region

```{r, results='asis'}
fin_dat %>% 
  ungroup() %>% 
  filter(n_add >= 100) %>% 
  group_by(cntry)  %>% 
  arrange(cntry, desc(prop_region_targeted)) %>% 
  slice(1:10) %>%
  filter(prop_region_targeted != 0) %>% 
  select(advertiser_name, cntry, mean_spend_per_ad, prop_age_targeted, prop_gender_targeted, prop_region_targeted) %>% 
  group_split(cntry) %>% 
  map(knitr::kable)
  
```

## Correlation between Gender and Age targeted

```{r}
fin_dat %>% 
  filter(n_add >= 10) %>% 
  ggplot(aes(prop_gender_targeted, prop_age_targeted)) +
  geom_point() +
  theme_minimal()
```

